An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-25 paper/paper.tex
Paper: Finish the Introduction

% highlights of methodology

% key results and conclusions

>>>>

% highlights of methodology
In order to determine whether or not our system provides solutions for the challenges of both P2P and centralized backup systems, we created test scenarios that test how well our system handles these challenges. We first tested how BitTorrent Sync handles a varying number of files to backup by backing 1G of data split up into 1 1GB file, 10 100MB files, and 100 10MB files and measuring the rates of data transfer over time. This was done on a network with just enough peers to have one file backed up with sufficient replication.

The second test scenario that we performed tested our system in a more realistic environment. Each instance of this scenario involved creating 100 peers on a network using MTA SZTAKI's cloud computing environment: SZTAKI Cloud. This scenario measured the effects of node churn, or the rate at which nodes go on and offline, on our system. Specifically, we measure how much network traffic is generated due to churn, since node unavailability is handled by moving replicas to different nodes. We take this measurement by running a test instance with no churn, and then running another where nodes periodically start and stop our BTBackup program. To make the test environment more realistic, we had each peer limit their download and upload speeds to values that are based off of worldwide Internet bandwidth statistics.

% key results and conclusions
After running our tests, we found that BTBackup, and by extension BitTorrent, performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that larger but fewer files are handled more efficiently than a greater number of smaller files, given the same amount of total data. We also determined that our system handles node churn well, when the rate of churn is modeled off of the average Internet user. Our final and most important result is that our system was able to achieve data transfer rates that are quicker than the rates that could be realistically achieved if the file transfers occurred between the peer and one other entity, which would be a central entity in a centralized backup system or one other peer in other P2P backup systems. This means that we can confidently conclude that BitTorrent is an excellent choice for the data transfer protocol in P2P backup systems.
